% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{hyperref}
\usepackage{color}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\begin{document} 

\name{Dylan Farvacque\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf Address} \\ 7220, 21\textsuperscript{st} Avenue, app \#205 \\ Montr\'{e}al, QC, H2A 2J5  \\ Canada. \\
 (438) 873-0497 }
\address{{\bf Email} \\ dylan.farvacque@polymtl.ca \\ {\href{https://ca.linkedin.com/in/dylanfarvacque}{\textcolor{blue}{\underline{My Linkedin}}}}}

\voffset = -20pt
\textwidth = 425pt
\footskip = 0pt

\begin{resume} 

  %Section competences 
  \section{Skills}
  %skills sur 2 colonnes
  \begin{ncolumn}{2}
    \bf{\underline{Languages:}} & \bf{\underline{Softwares:}} \\
    C/C++, Python, & Microsoft Visual Studio, \\
    C\#, XAML and Makefile,  & Emacs, \LaTeX, \\
    Bases of java and VHDL, & GNU/linux, \\
    Bases of HTML5,JS and CSS, & TFS, Git et SVN, \\
    Bases of x86 Assembly. & Netbeans. \\
    
  \end{ncolumn}

  
  %Sous-sec aptitudes general   
  {\bf General skills}
  \begin{itemize} \itemsep -3pt
  \item Take initiatives;
  \item Sense of responsibility, and well-organised;
  \item Capacity to adapt myself to a lot of situations, learn and apply fast;
  \end{itemize}
  \HRule

  %Sectoin honneur et reconnaissances
  \section{Honors \& \newline Awards}
  
  {\bf IEEEXtreme 8.0 competition} \hfill October 2014
  \begin{itemize} \itemsep -2pt
  \item World wide algorithms competition;
  \item Ranked 99\textsuperscript{th} out of 1852 teams;
  \item 24h programmation competition.
  \end{itemize}
  
  {\bf Recipient of the Philip \& Lily Malouf Prize} \hfill May 2014
  \begin{itemize} \itemsep -2pt
  \item Competition within the context of the first year integrative project;
  \item C/C++ embeded project.
  \item Finished 1st of the project.
  \end{itemize}
  
  {\bf ``Comp\'{e}tion informatique de Polytechnique Montr\'{e}al''} \hfill January 2014
  \begin{itemize} \itemsep -2pt
  \item Algorithms competition taking place during the computer science week in Polytechnique  Montr\'{e}al;
  \item Ranked 3rd as a first year student and 5th overall.
  \end{itemize}


  %Section implication externes
  \section{External Implications}
  
  {\bf STEP co-admin} \hfill June 2014 -
  \begin{itemize} \itemsep -3pt
  \item Maintain students' servers; \hfill to the day
  \item Update and maintain the STEP's website (rework in progress);
  \item On demand creation of mailing lists, repos and server space for students projects.
  \end{itemize}
  
  %Section Experience
  
  \section{Experiences}

  {\bf Software Developer,} \hfill May 2015 -\\
  Nventive, Montr\'eal, Canada \hfill to the day
  \begin{itemize} \itemsep -3pt  % reduce space between items
  \item Full time intern until end of august 2015, part time during semester;
  \item .Net Frontend developer;
  \item MVVM  architectural pattern;
  \item Use Rx and linq along with C\#.
  \end{itemize}
  
    
  %Section education

  \section{Education}
  
  {\bf Bachelor of software engineering (Expected May 2017)} \hfill 2013 -\\ 
  Polytechnique Montr\'{e}al \hfill to the day
  \begin{itemize} \itemsep -3pt
  \item Report card on demand.
  \end{itemize}
  
  

  %Section sport

  \section{Sports \\Results}
  
  {\bf General}
  \begin{itemize} \itemsep -2pt % reduce space between items
  \item Handball Martinique Champion division U9 (9years old);
  \item Gymnastics Martinique Champion division U10 and U11 (10-11 years old)
  \item Martinique Badminton Champion and inter-academy finalist division U12-U13 (12-13 years old)
  \item 2\textsuperscript{nd} of the ``Foul\'e de la St-Sylvestre'' (5km race) division U14-U15 (14-15 years old)
  \end{itemize}

  {\bf Tennis}
  \begin{itemize} \itemsep -2pt % reduce space between items

  \item Semi-finalist of St-Marie tournament division U13-U14 (13-14 years old);
  \item 2\textsuperscript{nd} round of the Spourtourne young tournament division U13-U14 (13-14 years old);
  \item 3\textsuperscript{rd} round of the Robert’s open tournament (all ages) at the age of 14;
  \item Martinique Vice-Champion of team tennis division U16 to U18 (16 to 18 years old) at the age of 15.
  \end{itemize}


\end{resume} 
\end{document} 



